Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-11 paper.tex
Ensure hyphens in cross-flow

% Abstract (Less than 200 words)
\abstract{The performance and wake characteristics of cross-flow (vertical axis)
    turbines depend on many parameters: solidity, blade profile, blade pitch, number
    of blades, strut drag, operational parameters such as tip speed ratio---and
    Reynolds number. Tolerable mismatch between physical model Reynolds number and
    full-scale Reynolds number was investigated from both the perspective of
    predicting full scale performance and flow dynamics, as well as numerical model
    validation. Experiments were performed with a large laboratory-scale cross flow
    turbine of to investigate Reynolds number dependence of performance and wake
    transport characteristics, and to determine what an acceptable Reynolds number
    mismatch is for scaled physical model tests of cross-flow turbines. It was
    demonstrated that the performance of the cross-flow turbine becomes essentially
    $Re$-independent at a Reynolds number based on turbine diameter of $Re_D \approx
    10^6$, or an approximate Reynolds number based on blade chord of $Re_c \approx 2
    \times 10^5$. A simple model that calculates peak torque coefficient from static
    foil data and cross-flow turbine kinematics was shown to be a reasonable
    estimator for predicting Reynolds number dependence of an actual cross flow
    turbine operating under dynamic conditions.}

>>>>

% Abstract (Less than 200 words)
\abstract{The performance and wake characteristics of cross-flow (vertical axis)
    turbines depend on many parameters: solidity, blade profile, blade pitch, number
    of blades, strut drag, operational parameters such as tip speed ratio---and
    Reynolds number. Tolerable mismatch between physical model Reynolds number and
    full-scale Reynolds number was investigated from both the perspective of
    predicting full scale performance and flow dynamics, as well as numerical model
    validation. Experiments were performed with a large laboratory-scale cross-flow
    turbine of to investigate Reynolds number dependence of performance and wake
    transport characteristics, and to determine what an acceptable Reynolds number
    mismatch is for scaled physical model tests of cross-flow turbines. It was
    demonstrated that the performance of the cross-flow turbine becomes essentially
    $Re$-independent at a Reynolds number based on turbine diameter of $Re_D \approx
    10^6$, or an approximate Reynolds number based on blade chord of $Re_c \approx 2
    \times 10^5$. A simple model that calculates peak torque coefficient from static
    foil data and cross-flow turbine kinematics was shown to be a reasonable
    estimator for predicting Reynolds number dependence of an actual cross-flow
    turbine operating under dynamic conditions.}
